Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-03 GECCO/volunteer-clouds-gecco16.tex
Little changes in the beginning of the methodology

We set up different experiments by deploying the server in free cloud
services, changing it from one experiment to the next if needed. This server runs a web service
which stores chromosomes sent from clients and serves requests to
them; it is 
an open source system that has been described extensively in
\cite{2016arXiv160101607Manom}. The client runs an evolutionary
algorithm written in JavaScript, that after a number of generations
sends the best individual back to the server, requesting at the same
time a random individual of those stored in the server. The experiment
starts by setting up a website that is sent by the server and announcing it on several social
networks so that people contribute to them by going to the page and
staying there for a while.

>>>>

We set up different experiments by deploying the server in free cloud
services, changing it from one experiment to the next if needed. This server runs a web service
which stores chromosomes sent from clients and serves requests to
them; it is 
an open source system that has been extensively described in
\cite{2016arXiv160101607Manom}. The client runs an evolutionary
algorithm written in JavaScript that after a number of generations
sends the best individual back to the server, requesting at the same
time a random individual of those stored in the server. The experiment
starts by setting up a website that is sent by the server and then announcing it on several social
networks so that people contribute to it by visiting the page and
staying there for a while.
